Automated topic naming to support cross-project analysis of software maintenance activities

### 2011-03-24 msr/msr2011.tex
Moved example and addressed log messages     - [X] The last sentence of the second paragraph of the second           column of the first page: Seems the example does not belong           here. Based on the sentence before the reader would expect           an example of how topic models help developers to get a           sense of project history.           - response: example has been moved to avoid confusion     - [X] Commit messages were used to extract the topics. It has not           discussed whether all commits have a log message (at least           for the two system which were studied).

Topic modeling is a machine learning technique which creates
multinomial distributions over words from a text corpus. 
The technique infers the hidden structure of a corpus using posterior
inference: the probability of the hidden structure given the data. 
Topic models are useful in software maintenance because they summarize
the key concepts in a corpus, such as source code, commit comments, or
mailing-list messages, by identifying statistically co-occurring words. 
Among other uses, it can quickly give developers an overview of where significant
activity has occurred, and gives managers or maintainers a sense of
project history. 
For example, a topic extracted from a set of commit logs might consist of the following terms: \emph{ ``listener change remove add fire''}. 
%A major challenge for topic modeling is to accurately identify the
%summary label for a topic; in the previous case, perhaps
%\emph{``event-handling''} would be appropriate. 
%Current approaches are manual: they rely on human expertise to
%recognize the appropriate label. 
%Furthermore, to date the results of topic modeling are project
%specific, and not generalizable. 
%This paper presents an approach, \emph{labelled topic extraction}, which addresses these two problems.

%migod
While machine learning techniques can automatically identify clumps of
commonly recurring terms, devising an appropriate summary label for
each clump/topic is harder.  
For example, the word list above might reasonably be labelled as
\emph{"event handling"} by a human who understands the domain well,
despite the fact that label does not appear in the word list itself.  
Current approaches to topic labelling rely on manual intervention by
human experts, and also are limited to project-specific topic labels.  
In this paper, we introduce \emph{labelled topic extraction}, an approach to topic labelling that is both automatic and creates labels that are project independent.

@@

For each project, we used source control commit comments, the messages
that programmers write when they commit revisions to a source control
repository. 
Commit comments are often studied by researchers, as they are the most readily accessible source of project interactions, and developers are often required to create them by the repository mechanism (e.g., Git).  Additionally, relying only on commit comments makes our approach more generalizable, as we do not assume the presence of other artifact corpora.
%This is the most readily accessible source of project interactions for outside researchers, since developers often or always (e.g., Git) write such message. Our approach is more generalizable if it does not assume the presence of other corpora. %bug trackers and email-list archives were not available for both projects. 
An example of a typical commit message, from MySQL, is: \textit{``history annotate diffs bug fixed (if mysql\-\_real\-\_connect() failed there were two pointers to malloc'ed strings, with memory corruption on free(), of course)''}. 
We extracted these messages and indexed them by creation time. 
We summarized each message as a word distribution but removed stop-words such as ``\emph{the}'' and ``\emph{at}''. 
%Stemming was performed in the later stages of our analysis. % WAS IT?

>>>>

Topic modeling is a machine learning technique which creates
multinomial distributions over words from a text corpus. 
The technique infers the hidden structure of a corpus using posterior
inference: the probability of the hidden structure given the data. 
Topic models are useful in software maintenance because they summarize
the key concepts in a corpus, such as source code, commit comments, or
mailing-list messages, by identifying statistically co-occurring words. 
Among other uses, it can quickly give developers an overview of where significant
activity has occurred, and gives managers or maintainers a sense of
project history. 
%A major challenge for topic modeling is to accurately identify the
%summary label for a topic; in the previous case, perhaps
%\emph{``event-handling''} would be appropriate. 
%Current approaches are manual: they rely on human expertise to
%recognize the appropriate label. 
%Furthermore, to date the results of topic modeling are project
%specific, and not generalizable. 
%This paper presents an approach, \emph{labelled topic extraction}, which addresses these two problems.

%migod
While machine learning techniques can automatically identify clumps of
commonly recurring terms, devising an appropriate summary label for
each clump/topic is harder.  
A given topic extracted from a set of commit logs might consist of the following terms: \emph{ ``listener change remove add fire''}. 
This topic might reasonably be labelled as
``\emph{event handling}'' by a human who understands the domain well,
despite the fact that label does not appear in the word list itself.  
Current approaches to topic labelling rely on manual intervention by
human experts, and also are limited to project-specific topic labels.  
In this paper, we introduce \emph{labelled topic extraction}, an approach to topic labelling that is both automatic and creates labels that are project independent.

@@

For each project, we used source control commit comments, the messages
that programmers write when they commit revisions to a source control
repository. 
Most commits we observed had commit comments.
Commit comments are often studied by researchers, as they are the most readily accessible source of project interactions, and developers are often required to create them by the repository mechanism (e.g., Git).  Additionally, relying only on commit comments makes our approach more generalizable, as we do not assume the presence of other artifact corpora.
%This is the most readily accessible source of project interactions for outside researchers, since developers often or always (e.g., Git) write such message. Our approach is more generalizable if it does not assume the presence of other corpora. %bug trackers and email-list archives were not available for both projects. 
An example of a typical commit message, from MySQL, is: \textit{``history annotate diffs bug fixed (if mysql\-\_real\-\_connect() failed there were two pointers to malloc'ed strings, with memory corruption on free(), of course)''}. 
We extracted these messages and indexed them by creation time. 
We summarized each message as a word distribution but removed stop-words such as ``\emph{the}'' and ``\emph{at}''. 
%Stemming was performed in the later stages of our analysis. % WAS IT?
